Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-07 implementation.tex
pass after rearrangement
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@953 ccdd05d5-56c1-461a-bf98-85f6876523b4

The \lloid\ algorithm could be used in a true sample-in-sample-out real-time
system.  However, such a system would likely require integration directly into
the data acquisition and storage system of the gravitational-wave
observatories.  A slightly more modest goal is to leverage existing low
latency, but not real-time, signal processing infrastructure in order to
implement the \lloid\ algorithm.  For the near-term this should be a viable 
solution for ultra-low latency searches with $\sim 1$s intrinsic latency.

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called \gstreamer\ \cite{gstreamer}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
gravitational-wave detector data to audio data it is not surprising that
\gstreamer\ is
useful for our purpose. \gstreamer\ also provides some useful stock signal
processing elements such as resamplers and filters.  We have extended the
\gstreamer\ framework by developing a library called \gstlal{}~\cite{gstlal}
that provides elements for gravitational-wave data analysis.
Figure~\ref{fig:pipeline} describes schematically how we implement the \lloid\
algorithm using \gstlal\ and \gstreamer\ components.

>>>>

The \lloid\ algorithm could be used in a true sample-in-sample-out real-time
system.  However, such a system would likely require integration directly into
the data acquisition and storage system of the gravitational-wave
observatories.  A slightly more modest goal is to leverage existing low
latency, but not real-time, signal processing infrastructure in order to
implement the \lloid\ algorithm.  For the near-term this should be a viable 
solution for ultra-low latency searches with order seconds of intrinsic latency.

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called \gstreamer\ \cite{gstreamer}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
gravitational-wave detector data to audio data it is not surprising that
\gstreamer\ is useful for our purpose. \gstreamer\ also provides some useful
stock signal processing elements such as resamplers and filters.  We have
extended the \gstreamer\ framework by developing a library called
\gstlal{}~\cite{gstlal} that provides elements for gravitational-wave data
analysis.
